---
title: "Project3"
author: "Group1: Min Jin, Atishay Sehgal, Wenting Yu, Lingyi Zhao, Yukun Pei"
date: "2018/10/23"
  html_notebook:
    df_print: paged
---

In your final repo, there should be an R markdown file that organizes **all computational steps** for evaluating your proposed image classification framework. 

This file is currently a template for running evaluation experiments of image analysis (or any predictive modeling). You should update it according to your codes but following precisely the same structure. 

```{r}
if(!require("EBImage")){
  source("https://bioconductor.org/biocLite.R")
  biocLite("EBImage")
}

if(!require("gbm")){
  install.packages("gbm")
}

if(!require("caret")){
  install.packages("caret")
}

library("EBImage")
library("gbm")
```


### Step 0: specify directories.

Set the working directory to the image folder. Specify the training and the testing set. For data without an independent test/validation set, you need to create your own testing data by random subsampling. In order to obain reproducible results, set.seed() whenever randomization is used. 

```{r wkdir, eval=FALSE}
set.seed(2018)
#setwd("./ads_fall2018_proj3") 
# here replace it with your own path or manually set it in RStudio to where this rmd file is located. 
# use relative path for reproducibility
```

Provide directories for training images. Low-resolution (LR) image set and High-resolution (HR) image set will be in different subfolders. 
```{r}
train_dir <- "../data/train_set/" # This will be modified for different data sets.
train_LR_dir <- paste(train_dir, "LR/", sep="")
train_HR_dir <- paste(train_dir, "HR/", sep="")
train_label_path <- paste(train_dir, "label.csv", sep="") 
```

### Step 1: set up controls for evaluation experiments.

In this chunk, we have a set of controls for the evaluation experiments. 

+ (T/F) cross-validation on the training set
+ (number) K, the number of CV folds
+ (T/F) process features for training set
+ (T/F) run evaluation on an independent test set
+ (T/F) process features for test set

```{r exp_setup}
run.cv=TRUE # run cross-validation on the training set
K <- 3  # number of CV folds
run.feature.train=TRUE # process features for training set
run.test=TRUE # run evaluation on an independent test set
run.feature.test=TRUE # process features for test set
```

Using cross-validation or independent test set evaluation, we compare the performance of models with different specifications. In this example, we use GBM with different `depth`. In the following chunk, we list, in a vector, setups (in this case, `depth`) corresponding to models that we will compare. In your project, you might compare very different classifiers. You can assign them numerical IDs and labels specific to your project. 

```{r model_setup}
# df -  is the feature combinations for baseline gbm
df <- data.frame(matrix(ncol = 3, nrow = 36))
x <- c("numTrees", "minNode", "shrinkage")
colnames(df) <- x

numTrees = seq(60, 110, 20) 
minNode = seq(5, 15, 3)
shrinkage = seq(0.05, 0.1, 0.02)

df$numTrees <- rep(numTrees, each = length(minNode)*length(shrinkage))
df$minNode <- rep(rep(minNode, each = length(shrinkage)), length(numTrees))
df$shrinkage <- rep(shrinkage, length(numTrees)*length(minNode))

model_values <- df
#model_labels = paste("GBM with numTrees =", model_values)
```

### Step 2: import training images class labels.

We provide extra information of image label: car (0), flower (1), market (2). These labels are not necessary for your model.

```{r train_label}
extra_label <- read.csv(train_label_path, colClasses=c("NULL", NA, NA))
```

### Step 3: construct features and responses

`feature.R` should be the wrapper for all your feature engineering functions and options. The function `feature( )` should have options that correspond to different scenarios for your project and produces an R object that contains features and responses that are required by all the models you are going to evaluate later. 
+ `feature.R`
  + Input: a path for low-resolution images.
  + Input: a path for high-resolution images.
  + Output: an RData file that contains extracted features and corresponding responses

```{r feature}
source("../lib/feature.R")

tm_feature_train <- NA
if(run.feature.train){
  tm_feature_train <- system.time(dat_train <- feature(train_LR_dir, train_HR_dir))
  feat_train <- dat_train$feature
  label_train <- dat_train$label
}

#save(dat_train, file="../output/feature_train.RData")
```


### Step 4: Train a classification model with training images
Call the train model and test model from library. 

`train.R` and `test.R` should be wrappers for all your model training steps and your classification/prediction steps. 
+ `train.R`
  + Input: a path that points to the training set features and responses.
  + Output: an RData file that contains trained classifiers in the forms of R objects: models/settings/links to external trained configurations.
+ `test.R`
  + Input: a path that points to the test set features.
  + Input: an R object that contains a trained classifier.
  + Output: an R object of response predictions on the test set. If there are multiple classifiers under evaluation, there should be multiple sets of label predictions. 
```{r loadlib}
source("../lib/train_baseline.R")
source("../lib/test_baseline.R")
```

#### Model selection with cross-validation
* Do model selection by choosing among different values of training model parameters, that is, the interaction depth for GBM in this example. 
```{r runcv, message=FALSE, warning=FALSE}
source("../lib/cross_validation_baseline.R")

if(run.cv){
  err_cv <- array(dim=c(nrow(model_values), 2))
  for(k in 1:nrow(model_values)){
    print(paste('Currently evaluating parameter combination ', k))
    
    cat("k=", k, "\n")
    err_cv[k,] <- cv.function(feat_train, label_train,  K, depth = 1, 
                              numTrees = model_values$numTrees[k] , 
                              minNode = model_values$minNode[k] , 
                              shrinkage = model_values$shrinkage[k])  
  }
  save(err_cv, file="../output/err_cv_baseline.RData")
}
```

Visualize cross-validation results. 
```{r cv_vis}
if(run.cv){
  load("../output/err_cv_baseline.RData")
  plot(1:36, err_cv[,1], xlab="minNode", ylab="CV Error",
     main="CV Error for BGM with depth = 1", type="n",xaxt = "n")
  axis(1, at=seq(1,36,by=1), labels=df$minNode)
  points(1:12, err_cv[1:12,1], col="red", pch=16)
  points(13:24, err_cv[13:24,1], col="blue", pch=16)
  points(25:36, err_cv[25:36,1], col="brown", pch=16)
  lines(1:36, err_cv[,1], col="black", type = 'b')
  legend("topright", legend=paste('numTrees = ', levels(as.factor(df$numTrees)) ), pch=16, col=c("red", "blue", "black"))

}

```


* Choose the "best"" parameter value
```{r best_model}
if(run.cv){
  model_best <- model_values[which.min(err_cv[,1]),]
}

par_best <- list(depth = 1, numTrees = model_best$numTrees, minNode = model_best$minNode,  shrinkage=model_best$shrinkage)

par_best
```

* Train the model with the entire training set using the selected model (model parameter) via cross-validation.
```{r final_train}
source("../lib/train_baseline.R")
tm_train=NA
tm_train <- system.time(fit_train <- train(feat_train, label_train, par_best))#, par_best
save(fit_train, file="../output/fit_train_baseline.RData")
```

### Step 5: Super-resolution for test images
Feed the final training model with the completely holdout testing data. 
+ `superResolution.R`
  + Input: a path that points to the folder of low-resolution test images.
  + Input: a path that points to the folder (empty) of high-resolution test images.
  + Input: an R object that contains tuned predictors.
  + Output: construct high-resolution versions for each low-resolution test image.
```{r superresolution}
source("../lib/superResolution.R")
test_dir <- "../data/test_set/" # This will be modified for different data sets.
test_LR_dir <- paste(test_dir, "LR/", sep="")
test_HR_dir <- paste(test_dir, "HR/", sep="")

tm_test=NA
if(run.test){
  load(file="../output/fit_train_baseline.RData")
  tm_test <- system.time(superResolution(test_LR_dir, test_HR_dir, fit_train))
}
```

### Summarize Running Time
Prediction performance matters, so does the running times for constructing features and for training the model, especially when the computation resource is limited. 
```{r running_time}
load("../output/err_cv_baseline.RData")
mse_baseline <- err_cv[which.min(err_cv[,1]),1]
PSNR_baseline <- 20 * log10(1) - 10 * log10(mse_baseline)
mse_baseline
PSNR_baseline

cat("Time for constructing training features=", tm_feature_train[1], "s \n")
#cat("Time for constructing testing features=", tm_feature_test[1], "s \n")
cat("Time for training model=", tm_train[1], "s \n")
cat("Time for super-resolution=", tm_test[1], "s \n")
```


